---
title: "Analysis of Edge.org Data"
author: "DMPE @ GitHub"
date: "August 5, 2017"
output: 
 html_notebook:
   css: report_styles.css
   highlight: haddock
   number_sections: yes
   theme: readable
   toc: yes
   toc_float:
     collapsed: no
     smooth_scroll: yes
     toc_depth: 3
editor_options:
  chunk_output_type: console
---

```{r setup, include=F}
library(knitr)
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

- In order to R Notebook HTML file, you have to execute this Rmd file in its directory/folder - not in the root! of repository `setwd("....where Rmd is located...") && rmarkdown::render("Edge.Rmd")`.

- The **source code** for this R Notebook can be found at GitHub: <https://github.com/dmpe/r>


# Objectives - Crowdsourcing Data Analysis 2

Description set out in <https://docs.google.com/document/d/1fXQBLdWydISskOKhoq8gl5unuwsv7VA3pkKY4IWFS6o/edit>.

In short, trying to confirm or rebut following:

> Hypothesis 1: "A woman's tendency to participate actively in the conversation correlates positively with the number of females in the discussion."

> Hypothesis 2: "Higher status participants are more verbose than are lower status participants."
 
When finished, report my results using this survey: <https://esmt.az1.qualtrics.com/jfe/form/SV_eaOyF0q39J6CVKZ>

## Variable Description of Data

**Type**: 1 for annual question, 2 for conversation

- Edge does an annual question every year; some examples are "what scientific idea is ready for retirement?" and "What will change everything?" People then write in with their answers. So all of the text is
written and asynchronous

- What Edge refers to as a conversation can actually be multiple things. Some of these are written essays by a single person, some are transcripts of a speech, and some are transcripts of a conversation (either between
two or more guests or an interview).

**AcademicHierarchyStrict** is described as:

1 = Graduate Student

2 = Postdoctoral

3 = Assistant Professor

4 = Associate Professor

5 = Professor

6 = Chaired Professor

**Limited_Information** is described as: equals 1 if we could only find limited information about the person 
(e.g. they commented in 2013 but we only have their job title from 2012), 0 otherwise

**Role**: Either author (=1) or commentator (=2)

**FemaleContributions**: the number of times a woman speaks in a specific conversation, it does not always equal the number of unique women in a conversation (see below)

**FemaleParticipation**: simply femalecontributors/(number of total contributions); the percentage of comments that are made by a woman

**Unique Contributors**: UniqueMaleContributors + UniqueFemaleContributors

**Unique Male Contributors**: the number of unique male contributors 

**Unique Female Contributors**: the number of unique female contributors

**Unique Female Participation**: the percentage of unique female participants; Unique Female Contributors divided by Unique Contributors

**Academic**: 1 = the person is in academia, 0 = they are not

**_Other_** columns are described in the corresponding **PDF** file. 

## Settings

You can control the default appearance with options:

- `options(tibble.print_max = n, tibble.print_min = m)`: if there are more than n rows, print only the first m rows. Use `options(tibble.print_max = Inf)` to always show all rows.

- `options(tibble.width = Inf)` will print all columns, regardless of the width of the screen.

From [vignette](https://cran.r-project.org/web/packages/tibble/vignettes/tibble.html):

```{r}
#options(tibble.print_max = Inf, tibble.width = Inf)
set.seed(1234)
```

## Loading libraries

```{r, message=FALSE, warning=FALSE}
# data wrangling
library(tidyverse)
library(reshape2)
library(scales)
library(tidyr)

# imputation & missingness
#library(mice)
#library(mi)
#library(Amelia)
library(VIM)

# markdown Rmd + table styling
library(kableExtra)

# for plotting - arranging/positioning
library(grid)
library(gridExtra)

# plotting
library(GGally)
library(ggthemes)
library(plotly)
```

## Read Data

```{r, eval=T, echo=T, warning=FALSE, message=FALSE}
edgeDS <- read_csv("edge1.1EditedFixed.csv", na = c("NA", "", " ", "#N/A"), trim_ws = T)
```

# First some pre-processing

## Deal with data problems

```{r, eval=T, echo=T}
# print(problems(edgeDS))

# I can either delete or fix row no. 1817 because it is broken mess. I fixed it in csv. 
# edgeDS <- edgeDS[-c(1817),]

# Replace 'Not Available' & 'Pending' with NA

edgeDS$PhD_Year[edgeDS$PhD_Year == "Not Available"] <- NA
edgeDS$PhD_Year[edgeDS$PhD_Year == "Pending"] <- NA
```

## Missing values

Number of rows that have some missing values:

```{r}
missing_data <- edgeDS[!complete.cases(edgeDS),]
nrow(missing_data) 
```

List variables with most missing values: 41 have some missing values, here are just TOP 10

```{r}
# delete those columns which contain...
mis <- edgeDS[, -grep("dummy|Unique|Contributions|Numerals", colnames(edgeDS))]

arrange(aggr(mis, col=mdc(1:2), numbers=TRUE, sortVars=TRUE, labels=names(mis), 
        cex.axis = .4, gap=3, prop = F, plot = F)$missings, desc(Count))[1:10, ]
```

```{r, eval=FALSE, echo=FALSE}
aggr(mis[, 1:90], col=mdc(1:2), numbers=TRUE, sortVars=TRUE, labels=names(mis), cex.axis=.4, gap=3, prop = F, plot = T)
missmap(mis)
head(md.pattern(mis))
```

```{r include=FALSE}
rm(mis, missing_data)
```

## Apply factors to various columns where it makes sense

And rename variable `Academic` from 0/1 to more descriptive Non_Academicians/Academicians

```{r}
cols <- c("Type", "Live", "Role", "TwoAuthors", "Limited_Information", 
          "Female", "Male", "Academic", "Job_Title_S", "Job_Title_S_num", 
          "Department_S" ,"Department_S_num" ,"Discipline", "HavePhD", 
          "AuthorAndCommenter", "PhD_Institution_SR_Bin", "Workplace_SR_Bin", 
          "SR_Ranking_Dif", "PhD_Institution_US_IR_Bin", "Workplace_US_IR_Bin", 
          "USA_I_Ranking_Dif", "PhD_Institution_US_Bin", "Workplace_US_Bin", 
          "USA_Ranking_Dif", "AcademicHierarchyStrict")

edgeDS[cols] <- lapply(edgeDS[cols], factor)
```

Transform two variables from **factor** to **character** to give them more meaning (similar to above).

```{r}
edgeDS$Academic <- recode(edgeDS$Academic, `1` = "Academicians", 
                          `0` = "Non_Academicians", .default = "Unknown")
edgeDS$Gender <- recode(edgeDS$Female, `1` = "Female", `0` = "Male", .default = "Unknown")
```

Drop now female & male columns and reorder data frame.

```{r}
edgeDS <- edgeDS[, !(names(edgeDS) %in% c("Female", "Male"))]
edgeDS <- edgeDS[, c(1,2,3,4,5,185,6:184)]
```

Potentially, transform year (do not evaluate though)

```{r, echo=TRUE, eval=FALSE}
numToChar <- function(x) { ux = unique(x); formatC(ux)[match(x, ux)] }
edgeDS$Year <- year(as.Date(numToChar(edgeDS$Year), "%Y"))
```

## Show data

What is the structure of dataset?

```{r}
str(edgeDS[,5:15])
```

Do not evaluate code below because the output would be too large. 

```{r,eval=FALSE, echo=T}
head(edgeDS)
summary(edgeDS) # print summaries of each variable
```

# My own questions

## How many times can a specific number of characters be observed?

**But first** take a broader look on the dataset. `tail()`/`head()` will report (i.e. print) only last/first 6 values. 

Who has contributed the most in all discussions ?

```{r}
tail(sort(table(edgeDS$Id))) 
```

How many unique participants are there ?

```{r}
length(unique(edgeDS$Id)) 
```

And overall number of unique values per each variable (printed only first and last 6)? 

```{r echo=FALSE}
kable(head(rapply(edgeDS,function(x)length(unique(x)))), "html") %>% 
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)

kable(tail(rapply(edgeDS,function(x)length(unique(x)))), "html") %>% 
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

And hey, look, that's **interesting**. While there are just 522 unique titles, there are 523 unique links. Using `count` function, I show number of observations (i.e. links) per title. 

And indeed, there are two same titles for different EDGE's conversations. [Preface from 2011](https://www.edge.org/conversation/preface) and [Preface from 2008](https://www.edge.org/conversation/preface-of-whats-next).

```{r}
count(edgeDS, Title, Link)[304:305, ]
count_numberOfChars_small <- arrange(count(edgeDS, Number.Characters)[, c(2,1)], desc(n))[1:20,]
count_numberOfChars <- arrange(count(edgeDS, Number.Characters)[, c(2,1)], desc(n))
```

Moreover, out of almost `r nrow(edgeDS)` observations, I can see that **`r percent(length(count_numberOfChars$n[count_numberOfChars$n == 1])/nrow(edgeDS))`** of comments has a lenght of **1**.

Another **`r percent(length(count_numberOfChars$n[count_numberOfChars$n == 2])/nrow(edgeDS))`** of comments has a character lenght of **2**.

```{r}
kable(head(count_numberOfChars_small, 10), "html",
      col.names = c("Number of comments...", "that have char lenght of...")) %>% 
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

The most common lenght of the comment is `r as.numeric(count_numberOfChars[1,2])` which occurs in `r as.numeric(count_numberOfChars[1,1])` comments.

A <strong>*parallel coordinate plot*</strong> shows how many times can a specific number of characters be observed. Here are only 20 vertices - "connections". I let the user figure out what is nicer and more understandable - I like the first one more.

```{r eval=T, echo=T, fig.height=8, fig.width=15, message=F, warning=F}
p1 <- ggparcoord(data = count_numberOfChars_small, columns = c(1, 2), scale = "globalminmax") + 
  scale_y_continuous(breaks = seq(0,60, by=2), 
                     sec.axis = sec_axis(~., name = "Number of characters", 
                                         breaks = seq(0,60, by=5))) + 
  labs(y = "Number of occurances", x = "", 
       title = "TOP 20 connections - from # of comments to lenght of comments") +
  scale_fill_ptol() + 
  theme_minimal() + 
  theme(axis.title.x=element_blank(), 
        axis.text.x=element_blank(), 
        axis.ticks.x=element_blank()) + 
  geom_segment(mapping = aes(x = 1, y = n, xend = 2, yend= Number.Characters), 
               inherit.aes = F, 
               data = count_numberOfChars_small, 
               arrow=arrow(length=unit(0.2,"cm")))

p2 <- ggparcoord(data = count_numberOfChars_small, columns = c(2, 1), scale = "globalminmax") + 
  scale_y_continuous(breaks = seq(0,60, by=2), 
                     sec.axis = sec_axis(~., name = "Number of occurances ", 
                                         breaks = seq(0,60, by=5))) + 
  labs(y = "Number of characters", x = "", 
       title = "TOP 20 connections - from lenght of comments to # of comments") +
  scale_fill_ptol() + 
  theme_minimal() + 
  theme(axis.title.x=element_blank(), 
        axis.text.x=element_blank(), 
        axis.ticks.x=element_blank()) + 
  geom_segment(mapping = aes(x = 1, y = Number.Characters, xend = 2, yend=n ), 
               inherit.aes = F, 
               data = count_numberOfChars_small, 
               arrow=arrow(length=unit(0.1,"cm")))
grid.arrange(p1, p2, ncol=2)
```

[Source 1](https://stackoverflow.com/a/27862149) / [Source 2](https://stackoverflow.com/a/29310738) / [GGPlot2 - geom_segment](http://ggplot2.tidyverse.org/reference/geom_segment.html)

## Relationship between debate size and academicians.

Namely, what is the relationship between number of all debaters and a group of academicians over the years?
Did it mean that if you participitated as an academician in the conversations, the debate size was also increasing? 

Let's find it out :) First, however, prepare the dataset.

```{r}
edgeDS_academiciansInDebates <- edgeDS %>% 
  filter(Type == 2) %>% # just "conversations" (not annual questions) written by either 1 or 2 authors
  select(Year, ThreadId, DebateSize, Academic) %>% 
  group_by_all() %>% 
  tally %>% 
  spread(Academic, n, fill = 0)
  
colnames(edgeDS_academiciansInDebates)[4] <- "NumberOf_Non_Academicians"
colnames(edgeDS_academiciansInDebates)[5] <- "NumberOf_Academicians"
colnames(edgeDS_academiciansInDebates)[6] <- "Unknown"
```

```{r echo=FALSE}
kable(head(edgeDS_academiciansInDebates, 3), "html") %>% 
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F) # table snippet
```

[Source for tally & spread code](https://stackoverflow.com/a/41735721)

How does debate size relate to the number of academicians? I make a simple linear regression to find out. 

```{r}
lm_aca_deb <- lm(DebateSize ~ NumberOf_Academicians, data = edgeDS_academiciansInDebates)
summary(lm_aca_deb)
```

The mean debate size will grow by `r lm_aca_deb$coefficients[2]` as the number of academicians increases by 1. 
If there are zero academicians, the debate size predicts to be `r lm_aca_deb$coefficients[1]`. 
[(Here is nice article on how to interpret LM)](https://onlinecourses.science.psu.edu/stat501/node/252)


Now, summarize number of academicians by year (from all conversations).

```{r}
year_aca_sum <- edgeDS_academiciansInDebates[,c(1,3,5)] %>% 
  group_by(Year) %>% 
  summarise(DebateSize = sum(DebateSize),
            NumberOf_Academicians_all = sum(NumberOf_Academicians), 
            Proportion = NumberOf_Academicians_all/DebateSize)
```

```{r echo=FALSE}
kable(head(year_aca_sum, 3), "html") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

```{r echo=FALSE, fig.height=8, fig.width=15}
g3 <- ggplot(year_aca_sum, aes(x = Year, y = NumberOf_Academicians_all)) + 
  geom_point() +
  geom_smooth(method = "lm", se = T, show.legend = TRUE, span = 0.3) +
  scale_x_continuous(breaks = pretty(year_aca_sum$Year, n = 19)) +
  scale_y_continuous(breaks = pretty(year_aca_sum$NumberOf_Academicians_all, 20)) + 
  scale_fill_ptol() + theme_minimal() +
  ggtitle("Number of academicians in all conversations per Year", 
          subtitle = "Has very small growing tendency.") + 
  ylab("Number of Academicians") 

g4 <- ggplot(year_aca_sum, aes(x = Year, y = Proportion)) + 
  geom_point() +
  geom_smooth(method = "lm", se = T, show.legend = TRUE, span = 0.3) +
  scale_x_continuous(breaks = pretty(year_aca_sum$Year, n = 19)) +
  scale_y_continuous(breaks = pretty(year_aca_sum$Proportion, 10)) + 
  scale_fill_ptol() + theme_minimal() +
  ggtitle("Proportion of academicians in debates", 
          subtitle = "by year. Has grown over the years quite significantly.") + 
  ylab("Number of Academicians/Debate Size") 

grid.arrange(g3, g4, ncol=2)
```

```{r, include=FALSE, echo=F, eval=F}
# And percentages ?
percantage <- percent(year_aca_sum$NumberOf_Academicians_all / year_aca_sum$DebateSize)
proportions_in_debates <- cbind(year_aca_sum$Year, percantage)
tail(proportions_in_debates) # show percentages from recent years
```
    
```{r, message=F, warning=F, eval=F, echo=F}
> Residuals are not symetrical and "that means that the model predicts certain points that fall far away from the actual observed points". [Source](https://feliperego.github.io/blog/2015/10/23/Interpreting-Model-Output-In-R)

> The model doesnt fit well the actual data. R^2 is low, hence correlation is also low - of just `r percent(summary(year_aca_sum_lm)$r.squared)`
```

## What is proportion of contributors in debates?

Let's now look on how different groups contribute in debates.

First, I start with (non-)academicians and hence need the right data.

```{r}
year_aca_byGroup <- edgeDS_academiciansInDebates[,c(1,3,4,5,6)] %>% 
  group_by(Year) %>% 
  summarise(DebateSize = sum(DebateSize), 
            Academicians = sum(NumberOf_Academicians), 
            Non_Academicians = sum(NumberOf_Non_Academicians), 
            Unknown = sum(Unknown))
```

```{r echo=FALSE}
kable(head(year_aca_byGroup), "html") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

Clearly, **academicians prevail in majority** of debates as the number of outsiders (non-aca + unknown) declined 
significantly over last few years. 

Also, the number of participitants in debates does not grow much - the summary statistics are: 
`r summary(year_aca_byGroup[2])`. The mean size of conversations is just shy of 300.

```{r fig.height=8, fig.width=15, message=F, warning=F}
year_aca_byGroup.long <- melt(year_aca_byGroup, id.vars = c(1,2))

k1 <- ggplot(data = year_aca_byGroup.long, aes(x = Year, y = value, fill = variable)) + 
  geom_col(position = position_stack(reverse = TRUE)) + 
  geom_line(aes(x = Year, y=DebateSize), data=year_aca_byGroup.long) +
  scale_y_continuous(breaks = seq(0, 1300, by = 100)) + 
  ggtitle("Number and type of debaters per year") + 
  labs(y = "Number of Participitans") +
  theme_minimal() + scale_fill_ptol() + 
  theme(legend.position="none")

year_aca_byGroup.long$variable <- factor(year_aca_byGroup.long$variable, 
                                         levels = c("Unknown","Non_Academicians","Academicians" , 
                                                    ordered = T))

k2 <- ggplot(year_aca_byGroup.long, aes(x = Year, y = value, fill = variable)) + 
    geom_bar(stat="identity", position="fill") + 
    scale_y_continuous(breaks = seq(0,1,by=0.1), labels = percent) +
    labs(y = "Percent", fill = "Type", title = "Debaters' proportionality per year by background") + 
    theme_minimal() + # scale_fill_ptol() +
    scale_fill_manual(
      values=c("Academicians"="#4477AA", "Non_Academicians"="#DDCC77", "Unknown"="#CC6677")) +
    scale_colour_manual(
      values=c("Academicians"="#4477AA", "Non_Academicians"="#DDCC77", "Unknown"="#CC6677"), 
      labels=c("Academicians", "Non_Academicians", "Unknown")) +
    labs(fill = "Group")
grid.arrange(k1, k2, ncol=2)
```

[Source #1 unused](https://stackoverflow.com/a/37818965) / [Source #2 position fill](https://stackoverflow.com/a/11026432) / [Source #3 for Percent bar plot](http://www.r-graph-gallery.com/48-grouped-barplot-with-ggplot2/) / [Source #4 for position_stack reverse](https://stackoverflow.com/a/34637703) / [Source #5 for deleting first legend](https://stackoverflow.com/a/35622358)


The same now with gender. 

```{r, message=F, warning=F}
edgeDS_genderInDebates <- edgeDS %>% 
  filter(Type == 2) %>% # just "conversations" (not annual questions) written by either 1 or 2 authors
  select(Year, ThreadId, DebateSize, Gender) %>% 
  group_by_all() %>% 
  tally %>% 
  spread(Gender, n, fill = 0)

colnames(edgeDS_genderInDebates)[6] <- "Unknown"
edgeDS_genderInDebates.long <- melt(edgeDS_genderInDebates, id.vars = c(1,2,3))
edgeDS_genderInDebates.long$variable <- factor(edgeDS_genderInDebates.long$variable, 
                                               levels = c("Unknown","Female","Male" , ordered = T))

ggplot(edgeDS_genderInDebates.long, aes(x = Year, y = value, fill = variable)) + 
    geom_bar(stat="identity", position="fill") + 
    scale_y_continuous(breaks = seq(0,1,by=0.05), labels = percent) +
    labs(y = "Percent", fill = "Type", title = "Debaters' proportionality per year by Gender") + 
    theme_minimal() + 
    scale_fill_manual(
      values=c("Male"="#4477AA", "Female"="#DDCC77", "Unknown"="#CC6677")) +
    scale_colour_manual(
      values=c("Male"="#4477AA", "Female"="#DDCC77", "Unknown"="#CC6677"), 
      labels=c("Male", "Female", "Unknown")) +
    labs(fill = "Gender")
```

In recent years, after 2010, number of women has increased somewhat. 

```{r include=FALSE, message=F, warning=F}
# Now, remove datasets to free RAM
rm(count_numberOfChars, year_aca_byGroup.long, year_aca_sum, edgeDS_academiciansInDebates, edgeDS_genderInDebates,
   g3,g4,lm_aca_deb,p1,p2,year_aca_byGroup, k1, k2, count_numberOfChars_small, edgeDS_genderInDebates.long)
```


# Hypothesis No. 1: Women's tendency 

> Hypothesis 1: "A woman's tendency to participate actively in the conversation correlates positively with the number of (i guess unique) females in the discussion."

I start however first with a broad look on the data. Hence, I create data that can be used later (prints only 5 columns). 

```{r}
edgeDS_conversations <- edgeDS %>% 
  filter(Type == 2) %>% 
  select(-Link, -Title, -Order, -Text,-Limited_Information, -starts_with("dummy")) %>% 
  select(-(62:144))
```

```{r echo=FALSE}
kable(head(edgeDS_conversations[,1:5]), "html") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

## Does the ratio of men/women increase over the years ?

What is number of contributions (# of comments) and unique people who contribute by gender per year.

```{r}
edgeDS_conversations_q1 <- edgeDS_conversations %>% 
  select(Year, ThreadId, Male_Contributions, Female_Contributions, UniqueMaleContributors, UniqueFemaleContributors) %>% 
  group_by_all() %>%
  distinct(.keep_all = TRUE) %>% 
  group_by(Year) %>% 
  summarise(Total_Male_Contributions = sum(Male_Contributions),
            Total_Female_Contributions = sum(Female_Contributions),
            Total_Contributions = Total_Male_Contributions + Total_Female_Contributions,
            Total_UniqueMaleContributors = sum(UniqueMaleContributors), 
            Total_UniqueFemaleContributors = sum(UniqueFemaleContributors), 
            Total_Unique_Contributions = Total_UniqueMaleContributors + Total_UniqueFemaleContributors)
```

```{r echo=FALSE}
kable(head(edgeDS_conversations_q1), "html") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), font_size = 10)
```

**Explanation for hike in 2008**: The big spike would be attributed to the financial crises where I would assume that 
a lot of people were searching for job at home and had a lot of time to invest into Edge conversations. 

Both, the unique number of contributors (left plot) and total number of contributions in debates is growing for both genders - albeit just a little. 

```{r, fig.height=8, fig.width=15, message=F, warning=F }
r1 <- ggplot(edgeDS_conversations_q1, aes(x= Year)) + 
  geom_point(aes(y = Total_UniqueMaleContributors, colour = "Male Contr.")) + 
  geom_line(aes(y = Total_UniqueMaleContributors, colour = "Male Contr.")) +
  stat_smooth(aes(y = Total_UniqueMaleContributors, colour = "Male Contr."), 
              method = "lm", col = "#1695A3") + 
  geom_point(aes(y = Total_UniqueFemaleContributors, colour = "Female Contr.")) + 
  geom_line(aes(y = Total_UniqueFemaleContributors, colour = "Female Contr.")) +
  stat_smooth(aes(y = Total_UniqueFemaleContributors, colour = "Female Contr."), 
              method = "lm", col = "#450003") + 
  ylab("# of Unique people contributing by Gender") + labs(color = "Gender") + 
  ggtitle("Unique Contributors over years") +
  theme_minimal() + scale_fill_ptol() + theme(legend.position="none") +
  scale_x_continuous(breaks = pretty(edgeDS_conversations_q1$Year, n = 19)) + 
  scale_y_continuous(breaks = seq(0, 200, by = 25), limits = c(0, 200))

r2 <- ggplot(edgeDS_conversations_q1, aes(x= Year)) + 
  geom_point(aes(y = Total_Male_Contributions, colour = "Male Contr.")) + 
  geom_line(aes(y = Total_Male_Contributions, colour = "Male Contr.")) +
  stat_smooth(aes(y = Total_Male_Contributions, colour = "Male Contr."), 
              method = "lm", col = "#1695A3") + 
  geom_point(aes(y = Total_Female_Contributions, colour = "Female Contr.")) + 
  geom_line(aes(y = Total_Female_Contributions, colour = "Female Contr.")) +
  stat_smooth(aes(y = Total_Female_Contributions, colour = "Female Contr."), 
              method = "lm", col = "#450003") + 
  ylab("Total Contributions by Gender") + labs(color = "Gender") + 
  ggtitle("Total Contributions by Men are volatile", 
          subtitle = "While those by Women stay pretty much the same") +
  theme_minimal() + scale_fill_ptol() +
  scale_x_continuous(breaks = pretty(edgeDS_conversations_q1$Year, n = 19)) + 
  scale_y_continuous(breaks = seq(0, 1250, by = 100))

grid.arrange(r1, r2, ncol= 2)
```

[Source #1](https://stackoverflow.com/a/38938781), [Source #2](https://stackoverflow.com/a/10358388)

## Faceting on various variables

We can now look on how the participitation of women has increased over the years - considering that there might be 
differences between those in Academia with PhD. or where the author and commenter are the same person.  

The plot below shows e.g. that there are no women who are academicians and dont have their PhD. Every women is either academician with PhD. (makes sence) or is a non-academician with either PhD or without 

```{r, fig.height=8, fig.width=15, message=F, warning=F}
women_part_by_year <- edgeDS_conversations %>% 
  select(Year, Gender, Female_Contributions, Live, Academic, 
         TwoAuthors, HavePhD, AuthorAndCommenter) %>% 
  filter(Gender == "Female") %>% 
  group_by_all() %>% 
  tally %>% 
  spread(Gender, n, fill = 0)

women_part_by_year$Live <- ifelse(women_part_by_year$Live == 0, "Written TP", "Transcribed TP")
women_part_by_year$TwoAuthors <- ifelse(women_part_by_year$TwoAuthors == 1, "2 authors", "1 author")
women_part_by_year$HavePhD <- ifelse(women_part_by_year$HavePhD == 1, "Have PHD", "Don't have PHD")
women_part_by_year$AuthorAndCommenter <- ifelse(women_part_by_year$AuthorAndCommenter == 1,
                                                "Both author and commentator", "Otherwise")
colnames(women_part_by_year)[8] <- "#_of_Females"

men_part_by_year <- edgeDS_conversations %>% 
  select(Year, Gender, Male_Contributions, Live, Academic, 
         TwoAuthors, HavePhD, AuthorAndCommenter) %>% 
  filter(Gender == "Male") %>% 
  group_by_all() %>% 
  tally %>% 
  spread(Gender, n, fill = 0)

men_part_by_year$Live <- ifelse(men_part_by_year$Live == 0, "Written TP", "Transcribed TP")
men_part_by_year$TwoAuthors <- ifelse(men_part_by_year$TwoAuthors == 1, "2 authors", "1 author")
men_part_by_year$HavePhD <- ifelse(men_part_by_year$HavePhD == 1, "Have PHD", "Don't have PHD")
men_part_by_year$AuthorAndCommenter <- ifelse(men_part_by_year$AuthorAndCommenter == 1,
                                                "Both author and commentator", "Otherwise")
colnames(men_part_by_year)[8] <- "#_of_Males"


d1 <- ggplot(women_part_by_year, aes(x=Year, y = Female_Contributions)) + 
  geom_point() + facet_grid(Academic ~ HavePhD) + 
  theme_minimal() + scale_fill_ptol() + 
  ggtitle("Female contributions and impact of being academician with/out PhD.", 
          subtitle = "There are no women in the academicia without PhD.")

d2 <- ggplot(men_part_by_year, aes(x=Year, y = Male_Contributions)) + 
  geom_point() + facet_grid(Academic ~ HavePhD) + 
  theme_minimal() + scale_fill_ptol() + 
  ggtitle("Male contributions and impact of being academician with/out PhD.", 
          subtitle = "Here, there are actually men who dont have PhD. but are in academia")

grid.arrange(d1,d2,ncol=2)

d3 <- ggplot(women_part_by_year, aes(x=Year, y = Female_Contributions)) + 
  geom_point() + facet_grid(AuthorAndCommenter ~ TwoAuthors) + 
  theme_minimal() + scale_fill_ptol() + 
  ggtitle("Female contributions to the articles where the author and commenter is", 
          subtitle = "same person and where comments can be written by two people")

d4 <- ggplot(men_part_by_year, aes(x=Year, y = Male_Contributions)) + 
  geom_point() + facet_grid(AuthorAndCommenter ~ TwoAuthors) + 
  theme_minimal() + scale_fill_ptol() + 
  ggtitle("Male contributions to the articles where the author and commenter is", 
          subtitle = "same person and where comments can be written by up 2 people")

grid.arrange(d3,d4,ncol=2)

d5 <- ggplot(women_part_by_year, aes(x=Year, y = Female_Contributions)) + 
  geom_point() + facet_grid(Live ~ . ) + 
  theme_minimal() + scale_fill_ptol() + 
  ggtitle("Female contributions to the Transcribed or Written Text Pieces", 
          subtitle = "Relatively equally spread")

d6 <- ggplot(men_part_by_year, aes(x=Year, y = Male_Contributions)) + 
  geom_point() + facet_grid(Live ~ . ) + 
  theme_minimal() + scale_fill_ptol() + 
  ggtitle("Male contributions to the Transcribed or Written Text Pieces", 
          subtitle = "Relatively equally spread")

grid.arrange(d5,d6,ncol=2)
```

## Female participation per Year

Again prepare the data for later use.

```{r}
PeoplePerThreadID <- edgeDS_conversations %>% 
  select(Year, ThreadId, Male_Contributions, 
         Female_Contributions, FemaleParticipation, 
         DebateSize, UniqueContributors, UniqueMaleContributors, 
         UniqueFemaleContributors, UniqueFemaleParticipation) %>% 
  distinct(.keep_all = TRUE) %>% 
  select(Year, FemaleParticipation) %>% 
  group_by(Year) %>% 
  mutate(AvgFemaleParticipationPerYear = mean(FemaleParticipation),
         MedianFemaleParticipationPerYear = median(FemaleParticipation),
         SumFemaleParticipationPerYear = sum(FemaleParticipation))

ratio <- edgeDS_conversations_q1$Total_Female_Contributions/edgeDS_conversations_q1$Total_Contributions
```

Independanly of how one calculates the (avarage) female participitation, the trend is still growing. 

```{r, fig.height=8, fig.width=15, message=F, warning=F}
q1 <- ggplot(PeoplePerThreadID, aes(x = Year, y = AvgFemaleParticipationPerYear)) +
  geom_point() + 
  ggtitle("Female Participation per Year is slightly increasing", 
          subtitle = "Calculatation based on avaraging 'Female Participation' (from dataset)") +
  geom_line() + 
  ylab("Avarage Female Participation") +
  geom_smooth(method = "lm", se = T, show.legend = TRUE) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1), limits = c(0, 1)) +
  scale_x_continuous(breaks = pretty(PeoplePerThreadID$Year, n = 19)) +
  theme_minimal() + scale_fill_ptol() 

q2 <- ggplot(edgeDS_conversations_q1, aes(x=Year)) + geom_point(aes(y=ratio)) + geom_line(aes(y=ratio)) +
  ggtitle("Here it is also growing", 
          subtitle = "Calculatation based on total fe(male) contributions per year") +
  theme_minimal() + scale_fill_ptol() + ylab("Total_Female_Contributions/Total_Contributions") +
  scale_x_continuous(breaks = pretty(edgeDS_conversations_q1$Year, n = 19)) + 
  scale_y_continuous(breaks = seq(0, 1, by = 0.1), limits = c(0, 1))

grid.arrange(q1,q2, ncol=2)
```

## Correlations

For reminder:

> Hypothesis 1: "A woman's tendency to participate actively in the conversation correlates positively with the number of (i guess unique) females in the discussion."

```{r}
cor_data <- edgeDS %>% 
  filter(Role == 1, Gender == "Female", Type == 2) %>% 
  select(-Link, -Id_num, -ThreadId, -Year, -Title,-Role,-Type, 
         -Order, -Text,-Limited_Information,-Gender, -starts_with("dummy"))

all_factors_names <- as.data.frame(sapply(cor_data, is.factor))
all_factors_names$name <- rownames(all_factors_names)
all_factors_names <- all_factors_names[all_factors_names$`sapply(cor_data, is.factor)` == TRUE,]
cor_data <- cor_data[ , !(names(cor_data) %in% all_factors_names$name)]


all_char_names <- as.data.frame(sapply(cor_data, is.character))
all_char_names$name <- rownames(all_char_names)
all_char_names <- all_char_names[all_char_names$`sapply(cor_data, is.character)` == TRUE,]
cor_data <- cor_data[ , !(names(cor_data) %in% all_char_names$name)]
cor_data <- cor_data[ , -c(26:106)]


M <- cor(as.data.frame(cor_data), use = "pairwise.complete.obs")
```

**Idea**: If an author is a woman, then there is potentially a higher engagement with other women as well (those could be more interesting to contribute). 

**Result**: Yet correlation - at least for the case of Female Contributions - doesnt confirm this. 

```{r}
cor(cor_data$Female_Contributions, cor_data$UniqueFemaleContributors)
```

This is opposite with Female Participation where there is a strong correlation between the *normal* Female Participation ratio and the *unique* one.

```{r}
cor(cor_data$FemaleParticipation, cor_data$UniqueFemaleParticipation)
```

Plot correlation matrix.

```{r, fig.height=8, fig.width=15, message=F, warning=F}
corrplot(M)
ggcorr(M, nbreaks = 6, palette = "RdGy", label = TRUE, label_size = 3, 
       label_color = "white", hjust = 0.75, size = 2.5, angle = -5,layout.exp = 5)
```

```{r include=FALSE, message=F, warning=F}
# Now, remove datasets to free RAM
rm(PeoplePerThreadID,women_part_by_year, all_char_names,
   edgeDS_conversations_q1, q1,q2, r1, r2, all_factors_names, cor_data, d1,d2,d3,d4,d5,d6)
```


# Hypothesis No. 2: Verbosity 

> Hypothesis 2: "Higher status participants are more verbose than are lower status participants."

**My Definition of 'Status':** I define "higher status" as being solely dependent on the person's background, workplace (i.e. where (s)he comes from), his/her job (and if academicians, then also the department, discipline, academic rank and  citations) and whether (s)he has a PhD and from which institution, etc. I use data from the dataset, exclusively.  

```{r}
edgeDS_verbosity <- edgeDS %>% 
  select(Year, Academic, Limited_Information, H_Index, i10_Index, Role, Gender, 
         HavePhD, DebateSize, Job_Title_S, Department_S, Discipline, 
         PhD_Institution_SR_Bin, AcademicHierarchyStrict, Number.Characters) %>% 
  group_by_all()
```

## Look at different variables and how they impact how much people write to conversation and annual questions.

*Academia* <> Number of characters

```{r}
ggplotly(
  ggplot(edgeDS_verbosity, aes(Academic, Number.Characters)) + geom_boxplot() + 
  scale_y_continuous(breaks = seq(0,1000, by = 100), limits = c(0,1000)) + 
  xlab("Group") + ylab("Number of characters") + 
  ggtitle("Number of characters by group (both genders)") +
  theme_minimal() + scale_fill_ptol()
) %>% layout(xaxis = list(ticktext = c("Non_Academicians", "Academicians", "NA")))
```

Avarage number of characters by (non-)academicians:

```{r}
edgeDS_verbosity_aca_y <- edgeDS_verbosity %>% filter(Academic == "Academicians") 
mean(edgeDS_verbosity_aca_y$Number.Characters) 

edgeDS_verbosity_aca_n <- edgeDS_verbosity %>% filter(Academic == "Non_Academicians") 
mean(edgeDS_verbosity_aca_n$Number.Characters)
```
[Source #1](https://stackoverflow.com/a/4700136)


Does the number of characters in the comments depend anyhow on person's *job title*? Well, only slightly. 

```{r}
ggplotly(
  ggplot(edgeDS_verbosity, aes(Job_Title_S, Number.Characters)) + geom_boxplot() + 
    coord_flip() + 
    scale_y_continuous(breaks = seq(0,2000, by = 200), limits = c(0,2000)) +  
    xlab("Job Title") + ylab("Number of characters") + 
    ggtitle("Graduate students dont write any comments it seems", 
            subtitle = "maybe there are some in NA or Other bins") +
    theme_minimal() + scale_fill_ptol() 
)
```

Also, of those academic people, *departments/fields* they come from and work in - does it have any impact on how much they write?

```{r}
ggplotly(
  ggplot(edgeDS_verbosity, aes(Department_S, Number.Characters)) + geom_boxplot() + 
    coord_flip() + 
    scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x), 
                  labels = trans_format("log10", math_format(10^.x))) + 
    xlab("Academic Department") + ylab("Number of characters") + 
    theme_minimal() + scale_fill_ptol() 
)
```

*Discipline* also seems to have an impact. The difference between "Professions" and "Other" ("NA") is also quite significant.

```{r, echo=FALSE, eval=FALSE}
my_text <- "This text is at x=0.7 and y=0.8!"
my_grob = grid.text(my_text, x=0.7,  y=0.8, gp=gpar(col="firebrick", fontsize=14, fontface="bold"))
gg + annotation_custom(my_grob)
```



```{r, warning=F}
ggplotly(
  ggplot(edgeDS_verbosity, aes(Discipline, Number.Characters)) + 
    geom_boxplot() + coord_flip()  + 
    xlab("Academic Discipline") + ylab("Number of characters") + 
    scale_y_continuous(breaks = seq(0, 100000, by = 1000), limits = c(0, 10000)) + 
    stat_summary(fun.y="mean", geom="point", size=2.5, color="green") +  
    ggtitle("Box Plot of number of characters by academic discipline", 
         subtitle = "Green Point shows avarage/mean") +
    theme_minimal() + scale_fill_ptol()  
)

edgeDS_verbosity_disc_diff <- edgeDS_verbosity %>% 
  ungroup() %>% 
  select(Discipline, Number.Characters) %>% 
  group_by(Discipline) %>% 
  summarize(min_Number.Characters = min(Number.Characters), 
            #minDisciplineName = Discipline[which.min(Number.Characters)], 
            max_Number.Characters = max(Number.Characters), 
            #maxDisciplineName = Discipline[which.max(Number.Characters)]
            mean_Number.Characters = mean(Number.Characters)
            ) %>% 
  mutate(difference_max_min = maxNumber.Characters-minNumber.Characters)
```
[Source #1](https://stackoverflow.com/a/30196561)

```{r echo=FALSE}
kable(edgeDS_verbosity_disc_diff, "html") %>% 
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```


```{r}
ggplot(edgeDS_verbosity, aes(PhD_Institution_SR_Bin, Number.Characters)) + geom_boxplot() 

ggplot(edgeDS_verbosity, aes(AcademicHierarchyStrict, Number.Characters)) + geom_boxplot()

ggplot(edgeDS_verbosity, aes(Gender, Number.Characters)) + geom_boxplot()

ggplot(edgeDS_verbosity, aes(HavePhD, Number.Characters)) + geom_boxplot()  # More Verbose = yes
```

How much people with/out PhD write on avarage ?

```{r}
edgeDS_verbosity_hphd_y <- edgeDS_verbosity %>% filter(HavePhD == 1)
mean(edgeDS_verbosity_hphd_y$Number.Characters)

edgeDS_verbosity_hphd_n <- edgeDS_verbosity %>% filter(HavePhD == 0) 
mean(edgeDS_verbosity_hphd_n$Number.Characters)
```

Potentially, also interesting by role and debate size:

```{r}
ggplot(edgeDS_verbosity, aes(DebateSize, Number.Characters)) + geom_boxplot(aes(group = cut_width(DebateSize, 50)))

ggplot(edgeDS_verbosity, aes(Role, Number.Characters)) + geom_boxplot() 

gg_gender <- ggplot(edgeDS_verbosity, aes(Gender, Number.Characters)) + geom_boxplot()
# ggplotly(gg_gender, width = 672, height = 480)
```

Create bins for h-index and i10-index (**citations**)

```{r}
edgeDS_verbosity$hindex_bin <- cut(edgeDS_verbosity$H_Index, breaks=c(0,15, 30, 45, 60, 75, 90, 105, 120, 135, 150), labels=c("0-15","15-30","30-45", "45-60", "60-75", "75-90", "90-105", "105-120", "120-135", "135-150"))
ggplot(edgeDS_verbosity, aes(hindex_bin, Number.Characters)) + geom_boxplot() 

#TODO
edgeDS_verbosity$i10_bin <- cut(edgeDS_verbosity$i10_Index, breaks=seq(0,600, by = 40))
ggplot(edgeDS_verbosity, aes(i10_bin, Number.Characters)) + geom_boxplot() 
```










 categorize people into regions (e.g. according to schools/workplace) and show again number of chars ?
-> do americans write mroe than europeans ?




http://rpubs.com/marschmi/RMarkdown
https://raw.githubusercontent.com/marschmi/RMarkdown_May11_2016/master/RMarkdown_Lesson.Rmd


