---
title: "Analysis of Edge.org Data"
author: "DMPE @ GitHub"
date: "August 5, 2017"
output: 
 html_notebook:
   css: report_styles.css
   highlight: haddock
   number_sections: yes
   theme: readable
   toc: yes
   toc_float:
     collapsed: no
     smooth_scroll: yes
     toc_depth: 3
editor_options:
  chunk_output_type: console
---

```{r setup, include=F}
library(knitr)
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

# Objectives - Crowdsourcing Data Analysis 2

(you have to execute this Rmd file in its directory/folder - not in the root!)

Description set out in <https://docs.google.com/document/d/1fXQBLdWydISskOKhoq8gl5unuwsv7VA3pkKY4IWFS6o/edit>.

In short, trying to confirm or rebut following:

> Hypothesis 1: "A woman's tendency to participate actively in the conversation correlates positively with the number of females in the discussion."

> Hypothesis 2: "Higher status participants are more verbose than are lower status participants."
 
When finished, report my results using this survey: <https://esmt.az1.qualtrics.com/jfe/form/SV_eaOyF0q39J6CVKZ>

## Settings

You can control the default appearance with options:

- `options(tibble.print_max = n, tibble.print_min = m)`: if there are more than n rows, print only the first m rows. Use `options(tibble.print_max = Inf)` to always show all rows.

- `options(tibble.width = Inf)` will print all columns, regardless of the width of the screen.

From [vignette](https://cran.r-project.org/web/packages/tibble/vignettes/tibble.html):

```{r}
#options(tibble.print_max = Inf, tibble.width = Inf)
set.seed(1234)
```

## Loading huge number of libraries

```{r, message=FALSE, warning=FALSE}
# data wrangling
library(tidyverse)
library(reshape2)
library(scales)

# imputation & missingness
#library(mice)
#library(mi)
#library(Amelia)
library(VIM)

# markdown Rmd + table styling
library(kableExtra)

# for plotting - arranging/positioning
library(grid)
library(gridExtra)

# plotting
library(GGally)
library(ggthemes)
library(plotly)
```

## Read Data

```{r, eval=T, echo=T, warning=FALSE, message=FALSE}
edgeDS <- read_csv("edge1.1EditedFixed.csv", na = c("NA", "", " ", "#N/A"), trim_ws = T)
```

# First some pre-processing

## Deal with data problems


```{r, eval=T, echo=T}
# print(problems(edgeDS))

# I can either delete or fix row no. 1817 because it is broken mess. I fixed it in csv. 
# edgeDS <- edgeDS[-c(1817),]

# Replace Not Available & Pending with NA

edgeDS$PhD_Year[edgeDS$PhD_Year == "Not Available"] <- NA
edgeDS$PhD_Year[edgeDS$PhD_Year == "Pending"] <- NA
```

## Missing values

Number of rows that have some missing values

```{r}
missing_data <- edgeDS[!complete.cases(edgeDS),]
nrow(missing_data) 
```

```{r}
# delete those columns which contain...
mis <- edgeDS[, -grep("dummy|Unique|Contributions|Numerals", colnames(edgeDS))]

arrange(aggr(mis, col=mdc(1:2), numbers=TRUE, sortVars=TRUE, labels=names(mis), 
        cex.axis = .4, gap=3, prop = F, plot = F)$missings, desc(Count))[1:10, ] # 41 have some missing values
```

List variables with most missing values

```{r, eval=FALSE, echo=FALSE}
aggr(mis[, 1:90], col=mdc(1:2), numbers=TRUE, sortVars=TRUE, labels=names(mis), cex.axis=.4, gap=3, prop = F, plot = T)
missmap(mis)
head(md.pattern(mis))
```

```{r include=FALSE}
rm(mis, missing_data)
```

## Apply factors to various columns where it makes sense

And rename variable `Academic` from 0/1 to more descriptive

0 = Non_Academicians

1 = Academicians

```{r}
cols <- c("Type", "Live", "Role", "TwoAuthors", "Limited_Information", "Female", "Male", "Academic", "Job_Title_S", "Job_Title_S_num", "Department_S" ,"Department_S_num" ,"Discipline", "HavePhD", "AuthorAndCommenter", "PhD_Institution_SR_Bin", "Workplace_SR_Bin", "SR_Ranking_Dif", "PhD_Institution_US_IR_Bin", "Workplace_US_IR_Bin", "USA_I_Ranking_Dif", "PhD_Institution_US_Bin", "Workplace_US_Bin", "USA_Ranking_Dif", "AcademicHierarchyStrict")

edgeDS[cols] <- lapply(edgeDS[cols], factor)
```

Transform two variables from **factor** to **character** to give them more meaning.

```{r}
edgeDS$Academic <- recode(edgeDS$Academic, `1` = "Academicians", `0` = "Non_Academicians", .default = "Unknown")
edgeDS$Gender <- recode(edgeDS$Female, `1` = "Female", `0` = "Male", .default = "Unknown")
```

Drop now female & male columns and reorder data frame.

```{r}
edgeDS <- edgeDS[, !(names(edgeDS) %in% c("Female", "Male"))]
edgeDS <- edgeDS[, c(1,2,3,4,5,185,6:184)]
```

Potentially, transform year (not evaluated though)

```{r, echo=TRUE, eval=FALSE}
numToChar <- function(x) { ux = unique(x); formatC(ux)[match(x, ux)] }
edgeDS$Year <- year(as.Date(numToChar(edgeDS$Year), "%Y"))
```

## Shows some examples of data

What is the structure of dataset?

```{r}
str(edgeDS[,5:15])
```

Do not evaluate code below because the output would be huge. 

```{r,eval=FALSE, echo=T}
head(edgeDS)
summary(edgeDS) # print summaries of each variable
```

# My own questions

## How many times can a specific number of characters be observed?

**But first** take a broader look on the dataset. `tail()` will report (i.e. print) only last 6 values. 

Who has contributed the most in all discussions

```{r}
tail(sort(table(edgeDS$Id))) 
```

How many unique participants are there ?

```{r}
length(unique(edgeDS$Id)) 
```

And overall number of unique values per each variable (printed only first and last 6)? 

```{r echo=FALSE}
kable(head(rapply(edgeDS,function(x)length(unique(x)))), "html") %>% 
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)

kable(tail(rapply(edgeDS,function(x)length(unique(x)))), "html") %>% 
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

And hey, look, that's **interesting**. While there are just 522 unique titles, there are 523 unique links. Using `count` function, I show number of observations (i.e. links) per title. 

And indeed, there are two same titles for different EDGE's conversations. [Preface from 2011](https://www.edge.org/conversation/preface) and [Preface from 2008](https://www.edge.org/conversation/preface-of-whats-next).

```{r}
count(edgeDS, Title, Link)[304:305, ]
```

Moreover, out of almost 8000 observations, I can see that roughly the half of all comments are of the same length.

```{r}
count_numberOfChars <- arrange(count(edgeDS, Number.Characters)[, c(2,1)], desc(n))[1:20,]
kable(head(count_numberOfChars, 10), "html",
      col.names = c("Number of comments...", "that have char lenght of...")) %>% 
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

The most common lenght is `r as.numeric(count_numberOfChars[1,2])` which occurs in `r as.numeric(count_numberOfChars[1,1])` comments.


A <strong>*parallel coordinate plot*</strong> shows how many times can a specific number of characters be observed. Here are only 20 vertices - "connections". I let the user figure out what is nicer and more understandable - I like the first one more.

```{r eval=T, echo=T, fig.height=8, fig.width=15, message=F, warning=F}
p1 <- ggparcoord(data = count_numberOfChars, columns = c(1, 2), scale = "globalminmax") + 
  scale_y_continuous(breaks = seq(0,60, by=2), 
                     sec.axis = sec_axis(~., name = "Number of characters", breaks = seq(0,60, by=5))) + 
  labs(y = "Number of occurances", x = "", title = "TOP 20 connections - from lenght of comments to # comments") +
  scale_fill_ptol() + 
  theme_minimal() + 
  theme(axis.title.x=element_blank(), 
        axis.text.x=element_blank(), 
        axis.ticks.x=element_blank()) + 
  geom_segment(mapping = aes(x = 1, y = n, xend = 2, yend= Number.Characters), 
               inherit.aes = F, 
               data = count_numberOfChars, 
               arrow=arrow(length=unit(0.2,"cm")))

p2 <- ggparcoord(data = count_numberOfChars, columns = c(2, 1), scale = "globalminmax") + 
  scale_y_continuous(breaks = seq(0,60, by=2), 
                     sec.axis = sec_axis(~., name = "Number of occurances ", breaks = seq(0,60, by=5))) + 
  labs(y = "Number of characters", x = "", title = "TOP 20 connections - from # comments to lenght of comments") +
  scale_fill_ptol() + 
  theme_minimal() + 
  theme(axis.title.x=element_blank(), 
        axis.text.x=element_blank(), 
        axis.ticks.x=element_blank()) + 
  geom_segment(mapping = aes(x = 1, y = Number.Characters, xend = 2, yend=n ), 
               inherit.aes = F, 
               data = count_numberOfChars, 
               arrow=arrow(length=unit(0.1,"cm")))
grid.arrange(p1, p2, ncol=2)
```

[Source 1](https://stackoverflow.com/a/27862149) / [Source 2](https://stackoverflow.com/a/29310738) / [GGPlot2 - geom_segment](http://ggplot2.tidyverse.org/reference/geom_segment.html)

## Relationship between debate size and academicians.

Namely, what was the relationship between size of all debaters and a group of academicians over the years?
Did it mean that if you participitated as an academician in the conversations, the debate size was also increasing? 
Let's find it out :) First, however, prepare the dataset.

```{r}
edgeDS_academiciansInDebates <- edgeDS %>% 
  filter(Type == 2) %>% # just "conversations" (not annual questions) written by either 1 or 2 authors
  select(Year, ThreadId, DebateSize, Academic) %>% 
  group_by(Year, ThreadId, DebateSize, Academic) %>% 
  tally %>% 
  spread(Academic, n, fill = 0)
  
colnames(edgeDS_academiciansInDebates)[4] <- "NumberOf_Non_Academicians"
colnames(edgeDS_academiciansInDebates)[5] <- "NumberOf_Academicians"
colnames(edgeDS_academiciansInDebates)[6] <- "Unknown"
```

```{r echo=FALSE}
kable(head(edgeDS_academiciansInDebates, 3), "html") %>% 
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F) # table snippet
```

[Source for tally & spread code](https://stackoverflow.com/a/41735721)

How does debate size relate to the number of academicians? I make a simple linear regression to find out. 

```{r}
lm_aca_deb <- lm(DebateSize ~ NumberOf_Academicians, data = edgeDS_academiciansInDebates)
summary(lm_aca_deb)
```

So, the mean debate size will grow by `r lm_aca_deb$coefficients[2]` as the number of academicians increases by 1. 
If there are zero academicians, the debate size predicts to be `r lm_aca_deb$coefficients[1]`. 
[(Here is nice article on how to interpret LM)](https://onlinecourses.science.psu.edu/stat501/node/252)


Now, summarize number of academicians by year (from all conversations).

```{r}
year_aca_sum <- edgeDS_academiciansInDebates[,c(1,3,5)] %>% 
  group_by(Year) %>% 
  summarise(DebateSize = sum(DebateSize),
            NumberOf_Academicians_all = sum(NumberOf_Academicians), 
            Proportion = NumberOf_Academicians_all/DebateSize)
```

```{r echo=FALSE}
kable(head(year_aca_sum, 3), "html") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

```{r echo=FALSE, fig.height=8, fig.width=15}
g3 <- ggplot(year_aca_sum, aes(x = Year, y = NumberOf_Academicians_all)) + 
  geom_point() +
  geom_smooth(method = "lm", se = T, show.legend = TRUE, span = 0.3) +
  scale_x_continuous(breaks = pretty(year_aca_sum$Year, n = 19)) +
  scale_y_continuous(breaks = pretty(year_aca_sum$NumberOf_Academicians_all, 20)) + 
  scale_fill_ptol() + theme_minimal() +
  ggtitle("Number of academicians in all conversations per Year", 
          subtitle = "Has very small growing tendency.") + 
  ylab("Number of Academicians") 

g4 <- ggplot(year_aca_sum, aes(x = Year, y = Proportion)) + 
  geom_point() +
  geom_smooth(method = "lm", se = T, show.legend = TRUE, span = 0.3) +
  scale_x_continuous(breaks = pretty(year_aca_sum$Year, n = 19)) +
  scale_y_continuous(breaks = pretty(year_aca_sum$Proportion, 10)) + 
  scale_fill_ptol() + theme_minimal() +
  ggtitle("Proportion of academicians in debates", subtitle = "by year. Has grown over the years quite significantly.") + 
  ylab("Number of Academicians/Debate Size") 

grid.arrange(g3, g4, ncol=2)
```

```{r, include=FALSE, echo=F, eval=F}
# And percentages ?
percantage <- percent(year_aca_sum$NumberOf_Academicians_all / year_aca_sum$DebateSize)
proportions_in_debates <- cbind(year_aca_sum$Year, percantage)
tail(proportions_in_debates) # show percentages from recent years
```
    
```{r, message=F, warning=F, eval=F, echo=F}
> Residuals are not symetrical and "that means that the model predicts certain points that fall far away from the actual observed points". [Source](https://feliperego.github.io/blog/2015/10/23/Interpreting-Model-Output-In-R)

> The model doesnt fit well the actual data. R^2 is low, hence correlation is also low - of just `r percent(summary(year_aca_sum_lm)$r.squared)`
```


## What is proportion of contributors in debates?

Let's now look on how different groups contribute in debates.

First, the data.

```{r}
year_aca_byGroup <- edgeDS_academiciansInDebates[,c(1,3,4,5,6)] %>% 
  group_by(Year) %>% 
  summarise(DebateSize = sum(DebateSize), 
            Academicians = sum(NumberOf_Academicians), 
            Non_Academicians = sum(NumberOf_Non_Academicians), 
            Unknown = sum(Unknown))
```

```{r echo=FALSE}
kable(head(year_aca_byGroup), "html") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

Clearly, **academicians prevail in majority** of debates as the number of outsiders (non-aca + unknown) declined 
significantly over last few years. 
Also, the number of participitants in debates does not grow much - the summary statistics are: 
`r summary(year_aca_byGroup[2])`. The mean size of conversations is just shy of 300.

```{r fig.height=8, fig.width=15, message=F, warning=F}
year_aca_byGroup.long <- melt(year_aca_byGroup, id.vars = c(1,2))

k1 <- ggplot(data = year_aca_byGroup.long, aes(x = Year, y = value, fill = variable)) + 
  geom_col(position = position_stack(reverse = TRUE)) + 
  geom_line(aes(x = Year, y=DebateSize), data=year_aca_byGroup.long) +
  scale_y_continuous(breaks = seq(0, 1300, by = 100)) + 
  ggtitle("Number and type of debaters per year") + 
  labs(y = "Number of Participitans") +
  theme_minimal() + scale_fill_ptol() + 
  theme(legend.position="none")

year_aca_byGroup.long$variable <- factor(year_aca_byGroup.long$variable, levels = c("Unknown","Non_Academicians","Academicians" , ordered = T))

k2 <- ggplot(year_aca_byGroup.long, aes(x = Year, y = value, fill = variable)) + 
    geom_bar(stat="identity", position="fill") + 
    scale_y_continuous(breaks = seq(0,1,by=0.1), labels = percent) +
    labs(y = "Percent", fill = "Type", title = "Debaters' proportionality per year") + 
    theme_minimal() + # scale_fill_ptol() +
    scale_fill_manual(
      values=c("Academicians"="#4477AA", "Non_Academicians"="#DDCC77", "Unknown"="#CC6677")) +
    scale_colour_manual(
      values=c("Academicians"="#4477AA", "Non_Academicians"="#DDCC77", "Unknown"="#CC6677"), 
      labels=c("Academicians", "Non_Academicians", "Unknown"))

grid.arrange(k1, k2, ncol=2)
```

[Source #1 unused](https://stackoverflow.com/a/37818965) / [Source #2 position fill](https://stackoverflow.com/a/11026432) / [Source #3 for Percent bar plot](http://www.r-graph-gallery.com/48-grouped-barplot-with-ggplot2/) / [Source #4 for position_stack reverse](https://stackoverflow.com/a/34637703) / [Source #5 for deleting first legend](https://stackoverflow.com/a/35622358)

```{r include=FALSE, message=F, warning=F}
# Now, remove datasets to free RAM
rm(count_numberOfChars, year_aca_byGroup.long, year_aca_sum, edgeDS_academiciansInDebates,
   g3,g4,lm_aca_deb,p1,p2,year_aca_byGroup, k1, k2)
```



# Hypothesis No. 1: Women's tendency 

> Hypothesis 1: "A woman's tendency to participate actively in the conversation correlates positively with the number of (i guess unique) females in the discussion."

First, create data that can be used later (print only first 5 columns). 

```{r}
edgeDS_conversations <- edgeDS %>% 
  filter(Type == 2) %>% 
  select(-Link, -Title, -Order, -Text,-Limited_Information, -starts_with("dummy")) %>% 
  select(-(62:144))
```

```{r echo=FALSE}
kable(head(edgeDS_conversations[,1:5]), "html") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

```{r}
edgeDS_conversations_q1 <- edgeDS_conversations %>% 
  select(Year, ThreadId, Male_Contributions, Female_Contributions) %>% 
  group_by(Year, ThreadId, Male_Contributions, Female_Contributions) %>% 
  distinct(.keep_all = TRUE)
```

```{r echo=FALSE}
kable(head(edgeDS_conversations_q1), "html") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

Opportunities to group by: Live, Academia, Two authors, HavePhD, AuthorAndCommenter

## Does the ratio of men:women increase over year ?

Number of women per threadID/a single conversation

```{r}
ggplot(edgeDS_conversations_q1, aes(x= ThreadId)) + 
  geom_line(aes(y = Male_Contributions, colour = "Male Contributions")) + 
  geom_line(aes(y = Female_Contributions, colour = "Female Contributions")) + 
  ylab("Contributions by Gender") + labs(color = "Group")
# https://stackoverflow.com/a/38938781
```

```{r}
#ratio <- edgeDS_conversations_q1$Male_Contributions/edgeDS_conversations_q1$Female_Contributions
#ggplot(edgeDS_conversations_q1, aes(x=ThreadId)) + geom_line(aes(y=ratio))
```

ThreadId, Gender, Number of F + M in discussion ~ facet

```{r}
#edgeDS_conversations_q1.long <- melt(edgeDS_conversations_q1, id.vars = 2)

#ggplot(edgeDS_conversations_q1.long, aes(x = ThreadId, y = value)) +
 # geom_point() + facet_grid(. ~ variable)  + scale_y_log10()
```

Prepare data for later use.

```{r}
WomenPerThreadID <- edgeDS_conversations %>% 
  select(Year, ThreadId, Male_Contributions, 
         Female_Contributions, FemaleParticipation, 
         DebateSize, UniqueContributors, UniqueMaleContributors, 
         UniqueFemaleContributors, UniqueFemaleParticipation) %>% 
  distinct(.keep_all = TRUE)
```


## Female participation per Year

```{r}
WomenPerThreadID.q2 <- WomenPerThreadID %>% 
  select(Year, FemaleParticipation) %>% 
  group_by(Year) %>% 
  mutate(AvgFemaleParticipationPerYear = mean(FemaleParticipation))

ggplot(WomenPerThreadID.q2, aes(x = Year, y = AvgFemaleParticipationPerYear)) +
  geom_point() + ggtitle("Female Participation per Year", subtitle = "is slightly increasing") + ylab("Avarage Female Participation") +
  geom_smooth(method = "lm", se = T, show.legend = TRUE, span = 0.3) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1), limits = c(0, 1)) +
  scale_x_continuous(breaks = pretty(WomenPerThreadID.q2$Year, n = 19)) +
  theme_minimal() + scale_fill_ptol() 
```

# Hypothesis No. 2: Verbosity 

> Hypothesis 2: "Higher status participants are more verbose than are lower status participants."

**First Task:** Define what is the "status". 

**My Definition:** I define "higher status" as being solely dependent on the person's background, workplace (i.e. where he comes from), his/her job (and if academicians, then also the department, discipline and academic rank), whether (s)he has a PhD and from which institution. 


```{r}
edgeDS_verbosity <- edgeDS %>% 
  select(Year, Academic, Limited_Information, H_Index, i10_Index, Role, Gender, HavePhD, DebateSize, Job_Title_S, Department_S, Discipline, PhD_Institution_SR_Bin, AcademicHierarchyStrict, Number.Characters) %>% 
  group_by(Year, Academic, Limited_Information, H_Index, i10_Index, Role, Gender, HavePhD, DebateSize, Job_Title_S, Department_S, Discipline, PhD_Institution_SR_Bin,AcademicHierarchyStrict, Number.Characters)
```

## Compare people based on their Job Title, Academic Department & Discipline, etc. in terms of how much did they write to conversation and annual questions.

**AcademicHierarchyStrict** is described as:

1 = Graduate Student

2 = Postdoctoral

3 = Assistant Professor

4 = Associate Professor

5 = Professor

6 = Chaired Professor

**Limited_Information** is described as: equals 1 if we could only find limited information about the person 
(e.g. they commented in 2013 but we only have their job title from 2012), 0 otherwise

**Role**: Either author (=1) or commentator (=2)

<https://stackoverflow.com/a/4700136>

```{r}
# guessing: this is most relevant
ggplot(edgeDS_verbosity, aes(Academic, Number.Characters)) + geom_boxplot() + scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x))) + xlab("Group") + ylab("Number of characters") + theme_minimal() + scale_fill_ptol() 

edgeDS_verbosity_aca_y <- edgeDS_verbosity %>% filter(Academic == "Academicians") 
mean(edgeDS_verbosity_aca_y$Number.Characters) # avarage number of chars by academicians

edgeDS_verbosity_aca_n <- edgeDS_verbosity %>% filter(Academic == "Non_Academicians") 
mean(edgeDS_verbosity_aca_n$Number.Characters) # avarage number of chars by non-academicians
```

Does number of characters in the comment depend anyhow on the job title? Well, only slightly. 

```{r}
ggplot(edgeDS_verbosity, aes(Job_Title_S, Number.Characters)) + geom_boxplot() + coord_flip() + scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x))) + xlab("Job Title") + ylab("Number of characters") + theme_minimal() + scale_fill_ptol() 
```

Also, of those academic people, departments/fields they come from and work in has some impact on how much they write. 

```{r}
ggplot(edgeDS_verbosity, aes(Department_S, Number.Characters)) + geom_boxplot() + coord_flip() + scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x))) + xlab("Academic Department") + ylab("Number of characters") + theme_minimal() + scale_fill_ptol() 
```

Discipline also seems to have an impact. The difference between "Professions" and "Other" ("NA") is also quite significant.

```{r, echo=FALSE, eval=FALSE}
my_text <- "This text is at x=0.7 and y=0.8!"
my_grob = grid.text(my_text, x=0.7,  y=0.8, gp=gpar(col="firebrick", fontsize=14, fontface="bold"))
gg + annotation_custom(my_grob)
```


```{r, warning=F}
ggplot(edgeDS_verbosity, aes(Discipline, Number.Characters)) + 
  geom_boxplot() + coord_flip()  + 
  xlab("Academic Discipline") + ylab("Number of characters") + 
  scale_y_continuous(breaks = seq(0, 100000, by = 1000), limits = c(0, 10000)) + 
  stat_summary(fun.y="mean", geom="point", size=2.5, color="green") +  
  labs(title="Box Plot of number of characters by academic discipline", caption="Green Point shows avarage/mean") +
  theme_minimal() + scale_fill_ptol()  

edgeDS_verbosity_disc_diff <- edgeDS_verbosity %>% 
  ungroup() %>% 
  select(Discipline, Number.Characters) %>% 
  group_by(Discipline) %>% 
  summarize(minNumber.Characters = min(Number.Characters), 
            #minDisciplineName = Discipline[which.min(Number.Characters)], 
            maxNumber.Characters = max(Number.Characters), 
            #maxDisciplineName = Discipline[which.max(Number.Characters)]
            ) %>% 
  mutate(difference_max_min = maxNumber.Characters-minNumber.Characters)
```

```{r echo=FALSE}
kable(edgeDS_verbosity_disc_diff, "html") %>% 
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```


[Source](https://stackoverflow.com/a/30196561)

```{r}
ggplot(edgeDS_verbosity, aes(PhD_Institution_SR_Bin, Number.Characters)) + geom_boxplot() 

ggplot(edgeDS_verbosity, aes(AcademicHierarchyStrict, Number.Characters)) + geom_boxplot()

ggplot(edgeDS_verbosity, aes(HavePhD, Number.Characters)) + geom_boxplot()  # More Verbose = yes

edgeDS_verbosity_hphd_y <- edgeDS_verbosity %>% filter(HavePhD == 1) # how much those with PhD write ?
mean(edgeDS_verbosity_hphd_y$Number.Characters)
edgeDS_verbosity_hphd_n <- edgeDS_verbosity %>% filter(HavePhD == 0) # how much those without PhD write ?
mean(edgeDS_verbosity_hphd_n$Number.Characters)
```

Potentially, also interesting

```{r}
ggplot(edgeDS_verbosity, aes(DebateSize, Number.Characters)) + geom_boxplot(aes(group = cut_width(DebateSize, 50)))

ggplot(edgeDS_verbosity, aes(Role, Number.Characters)) + geom_boxplot() 

gg_gender <- ggplot(edgeDS_verbosity, aes(Gender, Number.Characters)) + geom_boxplot()
# ggplotly(gg_gender, width = 672, height = 480)
```

Create bins for h-index and i10-index (citations)

```{r}
edgeDS_verbosity$hindex_bin <- cut(edgeDS_verbosity$H_Index, breaks=c(0,15, 30, 45, 60, 75, 90, 105, 120, 135, 150), labels=c("0-15","15-30","30-45", "45-60", "60-75", "75-90", "90-105", "105-120", "120-135", "135-150"))
ggplot(edgeDS_verbosity, aes(hindex_bin, Number.Characters)) + geom_boxplot() 

#TODO
edgeDS_verbosity$i10_bin <- cut(edgeDS_verbosity$i10_Index, breaks=seq(0,600, by = 40))
ggplot(edgeDS_verbosity, aes(i10_bin, Number.Characters)) + geom_boxplot() 
```










 categorize people into regions (e.g. according to schools/workplace) and show again number of chars ?
-> do americans write mroe than europeans ?




http://rpubs.com/marschmi/RMarkdown
https://raw.githubusercontent.com/marschmi/RMarkdown_May11_2016/master/RMarkdown_Lesson.Rmd


