---
title: "Analysis of EDGE Data"
author: "DMPE @ GitHub"
date: "June 24, 2017"
output: 
  html_document: 
    df_print: default
    highlight: textmate
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks/Objectives - Crowdsourcing Data Analysis 2

Description set out in <https://docs.google.com/document/d/1fXQBLdWydISskOKhoq8gl5unuwsv7VA3pkKY4IWFS6o/edit>.

In short, tring too confirm or rebut following:

> Hypothesis 1: "A woman's tendency to participate actively in the conversation correlates positively with the number of females in the discussion."

> Hypothesis 2: "Higher status participants are more verbose than are lower status participants."
 
When finished, the goal is report my results using this (short) survey: <https://esmt.az1.qualtrics.com/jfe/form/SV_eaOyF0q39J6CVKZ>

## Settings

> You can control the default appearance with options:
- `options(tibble.print_max = n, tibble.print_min = m)`: if there are more than n rows, print only the first m rows. Use options(tibble.print_max = Inf) to always show all rows.
- `options(tibble.width = Inf)` will always print all columns, regardless of the width of the screen.

From [source](https://cran.r-project.org/web/packages/tibble/vignettes/tibble.html)

```{r}
#options(tibble.print_max = Inf)
#options(tibble.width = Inf)
```


## Loading huge number of libraries

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(plotly)
library(ggthemes)
library(reshape2)
library(scales)
library(corrplot)
library(mice)
library(mi)
library(VIM)
library(Amelia)
library(knitr)
library(kableExtra)
```

## Read Data

```{r, eval=T, echo=T, warning=FALSE, message=FALSE}
edgeDS <- read_csv("~/Downloads/edge1.1EditedFixed.csv", na = c("NA", "", " ", "#N/A"), trim_ws = T)
edgeDSsmall <- read_csv("~/Downloads/edge1.1EditedFixed.csv", na = c("NA", "", " ", "#N/A"), trim_ws = T)[1:30,]
```

## Pre-processing

### Deal with data problems


```{r, eval=T, echo=T}
# print(problems(edgeDS))

# Either delete or fix 1817 row. I fixed it in csv. 
# edgeDS <- edgeDS[-c(1817),] # delete row No. 1817 because it is broken mess


edgeDS$PhD_Year[edgeDS$PhD_Year == "Not Available"] <- NA
edgeDS$PhD_Year[edgeDS$PhD_Year == "Pending"] <- NA
```

`col_types = cols(PhD_Year = col_integer())` could have been now applied

### Missing values

```{r}
missing_data <- edgeDS[!complete.cases(edgeDS),]
nrow(missing_data) # number of rows that have some missing values

# delete those which start contain...
mis <- edgeDS[, -grep("dummy|Unique|Contributions|Numerals", colnames(edgeDS))]

# list variables with most missing values
arrange(aggr(mis, col=mdc(1:2), numbers=TRUE, sortVars=TRUE, labels=names(mis), 
        cex.axis = .4, gap=3, prop = F, plot = F)$missings, desc(Count))[1:45, ]

# aggr(mis[, 1:90], col=mdc(1:2), numbers=TRUE, sortVars=TRUE, labels=names(mis), cex.axis=.4, gap=3, prop = F, plot = T)
# missmap(mis)
# head(md.pattern(mis))
```

### Apply factors to various columns where it makes sence. 

Also rename variable Academic from 0/1 to 

0 = Non_Academicians

1 = Academicians

```{r}
cols <- c("Type", "Live", "Role", "TwoAuthors", "Limited_Information", "Female", "Male", "Academic", "Job_Title_S", "Job_Title_S_num", "Department_S" ,"Department_S_num" ,"Discipline", "HavePhD", "AuthorAndCommenter", "PhD_Institution_SR_Bin", "Workplace_SR_Bin", "SR_Ranking_Dif", "PhD_Institution_US_IR_Bin", "Workplace_US_IR_Bin", "USA_I_Ranking_Dif", "PhD_Institution_US_Bin", "Workplace_US_Bin", "USA_Ranking_Dif", "AcademicHierarchyStrict")

edgeDS[cols] <- lapply(edgeDS[cols], factor)
```

Transform 2 variables from **binary (factor)** to more **binary (character)** to give them more meaning.

```{r}
edgeDS$Academic <- recode(edgeDS$Academic, `1` = "Academicians", `0` = "Non_Academicians", .default = "Unknown")
edgeDS$Gender <- recode(edgeDS$Female, `1` = "Female", `0` = "Male")
```

Drop female & male columns and reorder dataframe

```{r}
edgeDS <- edgeDS[, !(names(edgeDS) %in% c("Female", "Male"))]
edgeDS <- edgeDS[, c(1,2,3,4,5,185,6:184)]
```

Potentially, transform year

```{r}
# numToChar <- function(x) { ux = unique(x); formatC(ux)[match(x, ux)] }
# edgeDS$Year <- year(as.Date(numToChar(edgeDS$Year), "%Y"))
```

### Shows some examples of data

```{r,eval=FALSE, echo=T}
head(edgeDS,1)
head(str(edgeDS))
```


### Summary of data

```{r, eval=FALSE, echo=T}
summary(edgeDS[,1:50])
```

## My own questions
`head()` will report only first 6 values 

```{r}
tail(sort(table(edgeDS$Id))) # Who has contributed the most in all discussions
length(unique(edgeDS$Id)) # How many unique participitants are there ?
```

And overall number of unique values per each variable ? 

```{r}
head(rapply(edgeDS,function(x)length(unique(x))))
```

## If you are academician, does it mean that the debate size will increase?

Let's find it out :) First, however, prepare the dataset.

```{r, eval=T}
edgeDS_academiciansInDebates <- edgeDS %>% 
  filter(Type == 2) %>% # just "conversations" (not annual questions) written by either 1 or 2 authors
  select(Year, ThreadId, DebateSize, Academic) %>% 
  group_by(Year, ThreadId, DebateSize, Academic) %>% 
  tally %>% 
  spread(Academic, n, fill = 0)
  
colnames(edgeDS_academiciansInDebates)[4] <- "NumberOf_Non_Academicians"
colnames(edgeDS_academiciansInDebates)[5] <- "NumberOf_Academicians"
colnames(edgeDS_academiciansInDebates)[6] <- "Unknown"

kable(head(edgeDS_academiciansInDebates))
```

[Source](https://stackoverflow.com/a/41735721)

Plot it!

```{r}
year_aca_sum <- edgeDS_academiciansInDebates[,c(1,5)] %>% 
  group_by(Year) %>% 
  summarise(NumberOf_Academicians_all = sum(NumberOf_Academicians))

kable(head(year_aca_sum), "html") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)


ggplot(year_aca_sum, aes(x = Year, y = NumberOf_Academicians_all)) + 
  geom_point() +
  geom_smooth(method = "lm", se = T, show.legend = TRUE, span = 0.3) +
  scale_x_continuous(breaks = pretty(year_aca_sum$Year, n = 19)) +
  scale_y_continuous(breaks = pretty(year_aca_sum$NumberOf_Academicians_all, 20)) + 
  scale_fill_ptol() + theme_minimal() +
  ggtitle("Number of academicians in all conversations per Year", 
          subtitle = "Has very small growing tendency. Or, well, rather random") + 
  ylab("Number of Academicians") 
```

Well, not so much. 

```{r}
year_aca_byGroup <- edgeDS_academiciansInDebates[,c(1,3,4,5,6)] %>% 
  group_by(Year) %>% 
  summarise(DebateSize = sum(DebateSize), 
            Academicians = sum(NumberOf_Academicians), 
            Non_Academicians = sum(NumberOf_Non_Academicians), 
            Unknown = sum(Unknown))

kable(head(year_aca_byGroup))

year_aca_byGroup.long <- melt(year_aca_byGroup, id.vars = c(1,2))

ggplot(year_aca_byGroup.long, aes(x = Year, y = value, fill = variable)) + 
  geom_col() + 
  scale_y_continuous(breaks = seq(0, 1300, by = 100)) + 
  ggtitle("Number and type of debaters per Year") + 
  ylab("Number of Participitans") + 
  labs(fill = "Type") + 
  theme_minimal() + scale_fill_ptol() 
```

## What is yearly proportion of academicians in debates?

```{r, echo=F}
percantage <- percent(year_aca_byGroup$Academicians / year_aca_byGroup$DebateSize)
proportions_in_debates <- cbind(year_aca_byGroup$Year, percantage)
```

```{r}
tail(proportions_in_debates) # show percentages from recent years
```


## Hypothesis No. 1: Participatation's tendency 

> Hypothesis 1: "A woman's tendency to participate actively in the conversation correlates positively with the number of (i guess unique) females in the discussion."

First, create tables that can be used later. 

```{r}
edgeDS_conversations <- edgeDS %>% 
  filter(Type == 2) %>% 
  select(-Link, -Title, -Order, -Text,-Limited_Information, -starts_with("dummy")) %>% 
  select(-(62:144))

kable(head(edgeDS_conversations[,1:5]), "html") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

```{r}
edgeDS_conversations_q1 <- edgeDS_conversations %>% 
  select(Year, ThreadId, Male_Contributions, Female_Contributions) %>% 
  group_by(Year, ThreadId, Male_Contributions, Female_Contributions) %>% 
  distinct(.keep_all = TRUE)

kable(head(edgeDS_conversations_q1), "html") %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), full_width = F)
```

Opportunities to group by: Live, Academia, Two authors, HavePhD, AuthorAndCommenter

### Does the ratio of men:women increase over year ?

```{r}
ggplot(edgeDS_conversations_q1, aes(x= ThreadId)) + 
  geom_line(aes(y = Male_Contributions, colour = "Male Contributions")) + 
  geom_line(aes(y = Female_Contributions, colour = "Female Contributions")) + 
  ylab("Contributions")
```

```{r}
ratio <- edgeDS_conversations_q1$Male_Contributions/edgeDS_conversations_q1$Female_Contributions
ggplot(edgeDS_conversations_q1, aes(x=ThreadId)) + geom_line(aes(y=ratio))
```


ThreadId, Gender, Number of F + M in discussion ~ facet

```{r}
edgeDS_conversations_q1.long <- melt(edgeDS_conversations_q1, id.vars = 2)

ggplot(edgeDS_conversations_q1.long, aes(x = ThreadId, y = value)) +
  geom_point() + facet_grid(. ~ variable)  + scale_y_log10()
```

### Number of women per threadID/conversation


```{r}
WomenPerThreadID <- edgeDS_conversations %>% 
  select(Year, ThreadId, Male_Contributions, Female_Contributions, FemaleParticipation, 
                                                    DebateSize, UniqueContributors, UniqueMaleContributors, UniqueFemaleContributors, UniqueFemaleParticipation) %>% 
  distinct(.keep_all = TRUE)
```


### Female participitation per Year

```{r}
WomenPerThreadID.q2 <- WomenPerThreadID %>% 
  select(Year, FemaleParticipation) %>% 
  group_by(Year) %>% 
  mutate(AvgFemaleParticipationPerYear = mean(FemaleParticipation))

ggplot(WomenPerThreadID.q2, aes(x = Year, y = AvgFemaleParticipationPerYear)) +
  geom_point() + ggtitle("Female Participation per Year", subtitle = "is slightly increasing") + ylab("Avarage Female Participation") +
  geom_smooth(method = "lm", se = T, show.legend = TRUE, span = 0.3) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1), limits = c(0, 1)) +
  scale_x_continuous(breaks = pretty(WomenPerThreadID.q2$Year, n = 19)) +
  theme_minimal() + scale_fill_ptol() 
```






## Hypothesis No. 2: Verbosity

> Hypothesis 2: "Higher status participants are more verbose than are lower status participants."

**First Task:** Define what is the "status". 

**My Definition:** I define "higher status" as being solely dependant on the person's background, workplace (i.e. where he comes from), his/her job (and if academicians, then also the department, discipline and academic rank), whether (s)he has a PhD and from which institution. 


```{r}
edgeDS_verbosity <- edgeDS %>% 
  select(Year, Academic, Limited_Information, H_Index, i10_Index, Role, Gender, HavePhD, DebateSize, Job_Title_S, Department_S, Discipline, PhD_Institution_SR_Bin, AcademicHierarchyStrict, Number.Characters) %>% 
  group_by(Year, Academic, Limited_Information, H_Index, i10_Index, Role, Gender, HavePhD, DebateSize, Job_Title_S, Department_S, Discipline, PhD_Institution_SR_Bin,AcademicHierarchyStrict, Number.Characters)
```

### Compare people based on their Job Title, Academic Department & Discipline, etc. in terms of how much did they write to conversation and annual questions.

**AcademicHierarchyStrict** is described as:

1 = Graduate Student

2 = Postdoctoral

3 = Assistant Professor

4 = Associate Professor

5 = Professor

6 = Chaired Professor

**Limited_Information** is described as: equals 1 if we could only find limited information about the person 
(e.g. they commented in 2013 but we only have their job title from 2012), 0 otherwise

**Role**: Either author (=1) or commentator (=2)

<https://stackoverflow.com/a/4700136>

```{r}
# guessing: this is most relevant
ggplot(edgeDS_verbosity, aes(Academic, Number.Characters)) + geom_boxplot() + scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x))) + xlab("Person in academia ?") + ylab("Number of characters")
edgeDS_verbosity_aca_y <- edgeDS_verbosity %>% filter(Academic == "Academicians") 
mean(edgeDS_verbosity_aca_y$Number.Characters)
edgeDS_verbosity_aca_n <- edgeDS_verbosity %>% filter(Academic == "Non_Academicians") 
mean(edgeDS_verbosity_aca_n$Number.Characters)

ggplot(edgeDS_verbosity, aes(Job_Title_S, Number.Characters)) + geom_boxplot() + coord_flip() + scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x))) + xlab("Job Title") + ylab("Number of characters")

ggplot(edgeDS_verbosity, aes(Department_S, Number.Characters)) + geom_boxplot() + coord_flip() + scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x))) + xlab("Academic Department") + ylab("Number of characters")

ggplot(edgeDS_verbosity, aes(Discipline, Number.Characters)) + geom_boxplot() + coord_flip() + scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x))) + xlab("Academic Discipline") + ylab("Number of characters")

ggplot(edgeDS_verbosity, aes(PhD_Institution_SR_Bin, Number.Characters)) + geom_boxplot() + scale_y_log10()

ggplot(edgeDS_verbosity, aes(AcademicHierarchyStrict, Number.Characters)) + geom_boxplot() + scale_y_log10()

ggplot(edgeDS_verbosity, aes(HavePhD, Number.Characters)) + geom_boxplot() + scale_y_log10(breaks = trans_breaks("log10", function(x) 10^x), labels = trans_format("log10", math_format(10^.x))) # More Verbose = yes
edgeDS_verbosity_hphd_y <- edgeDS_verbosity %>% filter(HavePhD == 1) 
mean(edgeDS_verbosity_hphd_y$Number.Characters)
edgeDS_verbosity_hphd_n <- edgeDS_verbosity %>% filter(HavePhD == 0) 
mean(edgeDS_verbosity_hphd_n$Number.Characters)
```

Potentially, also interesting

```{r}
ggplot(edgeDS_verbosity, aes(DebateSize, Number.Characters)) + geom_boxplot(aes(group = cut_width(DebateSize, 50)))
ggplot(edgeDS_verbosity, aes(Role, Number.Characters)) + geom_boxplot() + scale_y_log10()
gg_gender <- ggplot(edgeDS_verbosity, aes(Gender, Number.Characters)) + geom_boxplot() + scale_y_log10()
ggplotly(gg_gender, width = 672, height = 480)
```

Create bins for h-index and i10-index (citations)

```{r}
edgeDS_verbosity$hindex_bin <- cut(edgeDS_verbosity$H_Index, breaks=c(0,15, 30, 45, 60, 75, 90, 105, 120, 135, 150), labels=c("0-15","15-30","30-45", "45-60", "60-75", "75-90", "90-105", "105-120", "120-135", "135-150"))
ggplot(edgeDS_verbosity, aes(hindex_bin, Number.Characters)) + geom_boxplot() + scale_y_log10() 

#TODO
#edgeDS_verbosity$i10_bin <- cut(edgeDS_verbosity$i10_Index, breaks=c(0,15, 30, 45, 60, 75, 90, 105, 120, 135, 150), #labels=c("0-15","15-30","30-45", "45-60", "60-75", "75-90", "90-105", "105-120", "120-135", "135-150"))
#ggplot(edgeDS_verbosity, aes(i10_bin, Number.Characters)) + geom_boxplot() + scale_y_log10() 
```










 categorize people into regions (e.g. according to schools/workplace) and show again number of chars ?
-> do americans write mroe than europeans ?







