---
title: "Analysis of EDGE Data"
author: "DMPE"
date: "June 24, 2017"
output: 
  html_document: 
    df_print: default
    highlight: textmate
    number_sections: yes
    theme: readable
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks/Objectives

Try too confirm or rebut following:

> Hypothesis 1: "A woman's tendency to participate actively in the conversation correlates positively with the number of females in the discussion."

> Hypothesis 2: "Higher status participants are more verbose than are lower status participants."
 
When finished, report your results using this short survey <https://esmt.az1.qualtrics.com/jfe/form/SV_eaOyF0q39J6CVKZ>


## Settings
```{r}
options(tibble.print_max = Inf)
options(tibble.width = Inf)
```


## Libraries

```{r}
library(tidyverse)
library(ggplot2)
library(plotly)
library(ggthemes)
library(reshape2)
library(scales)
library(corrplot)
library(mice)
library(mi)
```

## Data

```{r, eval=T, echo=T}
edgeDS <- suppressWarnings(suppressMessages(read_csv("~/Downloads/edge1.1.csv", na = "NA")))
```

## Deal with data problems

`col_types = cols(PhD_Year = col_integer())` should not be applied because it is largely chars that are included

```{r, eval=FALSE, echo=F}
print(problems(edgeDS))
edgeDS[4305,23]
```


### Apply factors to various columns where it makes sence. 

Also rename variable Academic from 0/1 to 

0 = Non_Academicians

1 = Academicians

```{r}
cols <- c("Type", "Live", "Role", "TwoAuthors", "Limited_Information", "Female", "Male", "Academic", "Job_Title_S", "Job_Title_S_num", "Department_S" ,"Department_S_num" ,"Discipline", "HavePhD", "AuthorAndCommenter", "PhD_Institution_SR_Bin", "Workplace_SR_Bin", "SR_Ranking_Dif", "PhD_Institution_US_IR_Bin", "Workplace_US_IR_Bin", "USA_I_Ranking_Dif", "PhD_Institution_US_Bin", "Workplace_US_Bin", "USA_Ranking_Dif", "AcademicHierarchyStrict")

edgeDS[cols] <- lapply(edgeDS[cols], factor)

# transform academic variable

edgeDS$Academic <- recode(edgeDS$Academic, `1` = "Academicians", `0` = "Non_Academicians", .default = "Unknown")

# transform year
# numToChar <- function(x) { ux = unique(x); formatC(ux)[match(x, ux)] }
# edgeDS$Year <- year(as.Date(numToChar(edgeDS$Year), "%Y"))

```


## Shows some examples of data

```{r,eval=FALSE, echo=F}
head(edgeDS,1)
head(str(edgeDS))
```


## Summary of data
```{r, eval=FALSE, echo=F}
summary(edgeDS[,1:50])
```

## My own questions

```{r}
head(table(edgeDS$Id)) # Who many times have contributors voiced their opinions in all discussions
length(unique(edgeDS$Id)) # How many unique participitants are there ?
```

And overall number of unique values per each variable ? 

```{r}
head(rapply(edgeDS,function(x)length(unique(x))))
```

### Q2: If you are academician, does it mean that the debate size will increase?

Let's find it out :)


```{r, eval=T}
edgeDS_academiciansInDebates <- edgeDS %>% 
  filter(Type == 2) %>% # just "conversations"
  select(Year, ThreadId, DebateSize, Academic) %>% 
  group_by(Year, ThreadId, DebateSize, Academic) %>% 
  tally %>% 
  spread(Academic, n, fill = 0)
  
colnames(edgeDS_academiciansInDebates)[4] <- "NumberOf_Non_Academicians"
colnames(edgeDS_academiciansInDebates)[5] <- "NumberOf_Academicians"
colnames(edgeDS_academiciansInDebates)[6] <- "Unknown"
# <https://stackoverflow.com/a/41735721>

```

Plot it!

```{r}
year_aca_sum <- edgeDS_academiciansInDebates[,c(1,5)] %>% 
  group_by(Year) %>% 
  summarise(NumberOf_Academicians_all = sum(NumberOf_Academicians))

ggplot(year_aca_sum, aes(x = Year, y = NumberOf_Academicians_all)) + 
  geom_point() +
  geom_smooth(method = "lm", se = T, show.legend = TRUE, span = 0.3) +
  scale_x_continuous(breaks = pretty(year_aca_sum$Year, n = 19)) +
  scale_y_continuous(breaks = pretty(year_aca_sum$NumberOf_Academicians_all, 20)) + 
  scale_fill_ptol() + ggtitle("Number of academicians in all conversations per Year", subtitle = "has very small growing tendency. Or, well, rather random") + ylab("Number of Academicians") + 
  theme_minimal()
```


```{r}
year_aca_byGroup <- edgeDS_academiciansInDebates[,c(1,3,4,5,6)] %>% 
  group_by(Year) %>% 
  summarise(DebateSize = sum(DebateSize), 
            Academicians = sum(NumberOf_Academicians), 
            Non_Academicians = sum(NumberOf_Non_Academicians), 
            Unknown = sum(Unknown))

year_aca_byGroup.long <- melt(year_aca_byGroup, id.vars = c(1,2))

ggplot(year_aca_byGroup.long, aes(x = Year, y = value, fill = variable)) + 
  geom_col() + scale_y_continuous(breaks = seq(0, 1300, by = 100)) + 
  ggtitle("Number and type of debaters per Year") + ylab("Number of Participitans") + labs(fill = "Type") + theme_minimal() + scale_fill_ptol() 
```

#### What is proportion of academicians in the debate, per year ?

```{r, echo=F}
percantage <- percent(year_aca_byGroup$Academicians / year_aca_byGroup$DebateSize)
proportions_in_debates <- cbind(year_aca_byGroup$Year, percantage)
```

```{r}
head(proportions_in_debates, 7)
```


## Hypothesis 1: Conversations 

> Hypothesis 1: "A woman's tendency to participate actively in the conversation correlates positively with the number of (i guess unique) females in the discussion."

Opportunities to group by: Live, Academia, Two authors, HavePhD, AuthorAndCommenter

First, filter such a table. 

```{r}
edgeDS_conversations <- edgeDS %>% filter(Type == 2)
```

```{r}
table(edgeDS_conversations$Live)
```

### Number of women per threadID/conversation


```{r}
WomenPerThreadID <- edgeDS %>% 
  select(ThreadId, Male_Contributions, Female_Contributions, FemaleParticipation, 
                                                    DebateSize, UniqueContributors, UniqueMaleContributors, UniqueFemaleContributors, UniqueFemaleParticipation) %>% 
  distinct(.keep_all = TRUE)
```

















